Spin canonical rings of log stacky curves

### 2015-07-08 curves-write-up/spin_cring.tex
one more of brians comment to fill

\todo{Add example saying all congruence subgroups with a form of odd weight are generated in weight at most 5 with relations in weight at most 12, (which can be reduced to 10 if the signature is not (0;3,3,3,3;0). Further, if $L_X$ is effective, then generation will be in weight at most 3.}
\begin{example}
\label{eg:congruence-bounds}
Suppose $\Gamma \subset SL_2(\BZ)$ is a congruence subgroup. Then, since the action  of $SL_2(\BZ)$ has points with stabilizer order 2 and 3, the action of $\Gamma$ can only have points with stabilizer order 2 and 3. Furthermore, if $\Gamma$ has some odd weight modular form, then it must have no points with stabilizer order 2 (see Remark ~\ref{rem:odd-denom}). Therefore, by Corollary ~\ref{cor:main-mod-forms}, $M(\Gamma)$ is generated in degree at most $5$ with a relation in degree at most $12$. Furthermore, if the coarse space associated $\Gamma$ does not have .
\end{example}

>>>>

\begin{example}
\label{eg:congruence-bounds}
Suppose $\Gamma \subset SL_2(\BZ)$ is a congruence subgroup. Then, since 
the action  of $SL_2(\BZ)$ has points with stabilizer order 2 and 3, the 
action of $\Gamma$ can only have points with stabilizer order 2 and 3. 
Furthermore, if $\Gamma$ has some odd weight modular form, then it must 
have no points with stabilizer order 2 (see Remark ~\ref{rem:odd-denom}). 
Therefore, by Corollary ~\ref{cor:main-mod-forms}, $M(\Gamma)$ is 
generated in degree at most $5$ with relations in degree at most $12$. 
Furthermore, if the coarse space associated $\Gamma$ does not have, 
$(0;3,3,3,3;0),$ there are relations in degree at most $10$, as follows 
from the list of exceptional cases in Tables ~\ref{table:genus-0-exceptional-cases} and ~\ref{table:genus-0-exceptional}.
\end{example}
